---
title: "web scraping"
author: "krishna"
date: "18 March 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(corrplot)
library(tree)
library(randomForest)
library(caret)

ins=read.csv("C:\\Users\\Administrator\\Downloads\\insurance\\insurance.csv")

```

###To find the number of missing values
```{r}
colSums(is.na(ins))
str(ins)
```


###insurance claims is maximum in which region
```{r}
ins %>% group_by(region) %>% summarise(charges_paid=sum(charges)) %>% ggplot(aes(x=region,y=charges_paid))+geom_bar(stat = "identity",fill="steel blue")
```





###smokers
```{r}
ins %>% group_by(sex,region) %>% summarise(smokers=sum(smoker=="yes")) %>% ggplot(aes(x=region,y=smokers,fill=sex))+geom_bar(stat = "identity",position = "dodge")
```



###converting yes and no into numeric
```{r}
ins$smoker_num=ifelse(ins$smoker=="yes",1,0)
ins$smoker_num=as.factor(ins$smoker_num)
```

###correlation between different categories
```{r}
ins1=ins %>% select(-sex,-region,-smoker)
ins1 = ins %>% select(age, bmi, children, smoker_num, charges)
ins1$smoker_num=as.numeric(ins1$smoker_num)
corrplot(cor(ins1), method= "pie")



```


###smoker vs non smoker
```{r}
ggplot(data=ins,aes(x=smoker,y=charges,fill=smoker)) + geom_boxplot()
```

###concentration of smokers vs non smokers by region
```{r}
ins$smokers_vs_non=ifelse(ins$smoker_num==0,-1,1)
ggplot(data=ins,aes(x=region,y=smokers_vs_non))+geom_bar(stat='identity', aes(fill=smokers_vs_non))
```

###charges by different age group
```{r}
ins %>% group_by(sex,age) %>% summarise(total=sum(charges)) %>% ggplot(aes(x=age,y=total,col=sex))+geom_jitter(aes(size=total))
```




###charges based on bmi
```{r,warning=F}

for (i in 1:nrow(ins)) {
  if(ins$bmi[i]<18){
  ins$bmi_type[i] = "underweight"
}else if(ins$bmi[i]>30){
      ins$bmi_type[i] = "overweight"
}else{
       ins$bmi_type[i] = "normal"
}
}

ggplot(ins,aes(x=bmi_type,y=charges))+geom_boxplot(aes(fill=bmi_type))
```


###charges based on no of children
```{r}
ggplot(data = ins,aes(x=as.factor(children),y=charges))+geom_boxplot(aes(fill=children))
```
###charges based on age
```{r}
bins=cut(ins$age,breaks = 6)
ggplot(ins,aes(x=bins,y=charges))+geom_boxplot(aes(fill=bins))
```

```{r}
ins %>% select(age,charges) %>% ggplot(aes(x=age,y=charges))+geom_point()

```


### Linear regression ###
```{r}
ins$smoker_num=ifelse(ins$smoker=="yes",1,0)
ins1=ins %>% select(-sex,-region,-smoker)
ins1 = ins %>% select(age, bmi, children, smoker_num, charges)

ins1$child_cat = as.factor(ins1$children)

ins2 = ins1
ins_training=ins2[sample(1:1338,0.85*nrow(ins2)),]
ins_testing=ins2[sample(1:1338,0.15*nrow(ins2)),]


m1 = lm(charges~., data=ins_training %>% filter(smoker_num==0 ) %>% select(-smoker_num))
m2 = lm(charges~., data=ins_training %>% filter(smoker_num==1 ) %>% select(-smoker_num))


ins_testing$pred_hybrid = ifelse(ins_testing$smoker_num==0 ,
                          m1$coefficients[1]+ 
                          m1$coefficients[2]*ins_testing$age+ 
                          m1$coefficients[3]*ins_testing$bmi +
                          m1$coefficients[4]*ins_testing$children ,
                          
                          m2$coefficients[1]+
                          m2$coefficients[2]*ins_testing$age+
                          m2$coefficients[3]*ins_testing$bmi +
                          m2$coefficients[4]*ins_testing$children)

{{plot(ins_testing$charges, type='l')
  lines(ins_testing$pred_hybrid, col='red')}}

RMSE(ins_testing$charges, ins_testing$pred_hybrid)

```

### Linear regression with scaled data ###
```{r,warning=F}
ins2 = ins1 

s_dev=sd(ins2$charges)
mean_val=mean(ins2$charges)

ins2$bmi = scale(ins2$bmi)
ins2$charges=scale(ins2$charges)
ins_training=ins2[sample(1:1338,0.85*nrow(ins2)),]
ins_testing=ins2[sample(1:1338,0.15*nrow(ins2)),]

linear_model=lm(charges~.,data=ins_training)

ins_testing$pred_ins=predict(linear_model,ins_testing)

ins_testing$charges=(ins_testing$charges*s_dev)+mean_val
ins_testing$pred_ins=(ins_testing$pred_ins*s_dev)+mean_val

{{plot(ins_testing$charges,type = "l")
  lines(ins_testing$pred_ins,type = "l",col ="red")
}}

RMSE(ins_testing$charges, ins_testing$pred_ins)

```


### Decision tree to identify the factor which is affecting the most ###
```{r}
ins2 = ins1
ins_training=ins2[sample(1:1338,0.85*nrow(ins2)),]
ins_testing=ins2[sample(1:1338,0.15*nrow(ins2)),]

mod=tree(charges~.,data=ins_training)

ins_testing$pred=predict(mod,ins_testing)

{{plot(ins_testing$charges,type = "l",col = "blue")
lines(ins_testing$pred, type = "l",col ="red")}}
RMSE(ins_testing$pred,ins_testing$charges)

```

### Random forest ###
```{r}
ins2 = ins1
ins_training=ins2[sample(1:1338,0.85*nrow(ins2)),]
ins_testing=ins2[sample(1:1338,0.15*nrow(ins2)),]

mod=randomForest(charges~.,data=ins_training,ntree=500,mtry =3)

ins_testing$pred=predict(mod,ins_testing)


{{plot(ins_testing$charges,type = "l")
  lines(ins_testing$pred,type = "l",col ="red")
}}
RMSE(ins_testing$pred,ins_testing$charges)
```



